---
title: "Visualise half-life function"
author: "Vera Vinken"
date: "05/12/2023"
output: html_document
---
  
## Packages & functions 

```{r packages, include=TRUE, message=FALSE, warning=FALSE}

# Packages 
  library(truncnorm)
  library(ggplot2)
  library(data.table)
  library(foreach)
  library(doParallel)
  library(purrr)             # for making lists into dataframes 
  library(beepr)
  library(doParallel)         # For runing code parallel with dopar function 
  library(foreach)            # For running code parallel 
  library(ggpubr)             # To arrange plots 
  library(gridExtra)          # for grid.arrange 
  

# Function files 
  setwd("C:/Local_R/BiPhD-ABM/May23") # for hp elitebook 
  source('MOD_1_FuncSource.R')
  source('ModelSource.R')
```

## Background
The half-life function calculates how well a model performs in an environment. It takes the information about survival across all individuals across all timesteps. From here, it fits an exponential decay curve to see at which point in time half of the original individuals would be alive. 

## Run a model so you have data to work with 
```{r run a model, include=TRUE, message=FALSE, warning=FALSE}
  # environment model 
  env_func_1_1_par(days = 30, N= 1000, th_forage_sc = 0.008163265, daylight_h = 8, modelType = 11)

```

Now you have that outcome, I select the part of the outcome that goes into the half-life function. The halflife-function is specified in the Function Source file. 

```{r Put output into halflife function, include=TRUE, warning=FALSE, message=FALSE, echo=FALSE}
halflife_input<-output_env_func[[2]]

# This will do nothing, cause the function has not actual return output that is relevan there 
t_halflife_func(halflife_input = halflife_input)


# So do it step by step: 
for (i in 1:length(halflife_input)){
    if (i==1){
      # list for the t_HL
      t_HL_list<<-list()
      # list for general fit summaries
      fit_sum_list<-list()
    } 
    
    # Create the dataframe you'll be dealing with 
    df<-subset(halflife_input[[i]], halflife_input[[i]]$id=='alive')
    # clean up the dataframe
    df$timestep<-as.numeric(df$timestep)
    df<-df[,2:3]
    colnames(df)<-c('y', 't')
    
    # Now fit the model 
    
    # To control the interations in NLS I use the following 
    nls.control(maxiter = 100)
    # I use a basic exponential decay curve 
    # starting values need to be given 
    fit<-nls(y ~ a*exp(-b*t), data=df, 
             start=list(a=1, b=0.0000001))
    # pull out hte summary --> this has the estimated values for a an db in it 
    sum_fit<-summary(fit)
    # put in the list 
    fit_sum_list[[i]]<-sum_fit$parameters
    
    # Now, where does it cross the x-axis? 
    # Set the current a & b 
    cur_a<-fit_sum_list[[i]][1]
    cur_b<-fit_sum_list[[i]][2]
    # set the halflife 
    y_halflife<-0.5
    # now calculate the timestep at which this will occur 
    t_halflife<-(-(log(y_halflife/cur_a)/cur_b))
    # calculate y from there (just to check)
    ytest<-(cur_a*exp(-cur_b*t_halflife))
    
  }


```

Plot this to see what it looks like. 

```{r build the model function, include=TRUE, warning=FALSE, message=FALSE, results='hide'}
# The data we have 
plot(df$t, df$y, xlab="Timestep", ylab="Proportion alive")
curve(cur_a*exp(-cur_b*x), from = 0, to=2160, xlab="x", ylab="y", type="l", add=T)

# plot the curve on top 

points(df$t, df$y)


# plot the curve on top 
my_equation<-function(x){cur_a*exp(-cur_b*x)}

test<-ggplot(data.frame(x=c(1,2160)), aes(x=x))+
  stat_function(fun=my_equation)

ggplot(data=df, aes(x=df$t, y=df$y))+
  geom_line()+
  stat_function(fun=my_equation)
  
```

