---
title: "Develop pilferage function"
author: "Vera Vinken"
date: "15/09/2022"
output: html_document
---
  
## Packages 

```{r packages, include=TRUE, message=FALSE, warning=FALSE}
library(dplyr)        # For summarizing means across groups
library(SciViews)     # For the easy to use ln() function 
```

## Background
We decided to put pilferage in the model. No large effect is expected, but because other models in literature (Pravosudov & Lucas (2001)) use it, we will implement this as well. The halflife used is that of 20 days, which was observed by Brodin in 1994 and described in his paper from that year. The function should do the following: 

* Determine the decay constant (this will be set throughout simulatiosn as the halflife is set)
* Determine a probabilty that within 1 timestep 1 or more items will decay. 
* Then compare this to a randomly generated number between 0 and 1 
* If our probability is larger than this number, an item will decay (we assume just 1, as the probability that this is 2 or more is incredibly small)
* cache number needs to be updated accordingly 

## Exploring the basic functionality 
Here I use the maths as they are used for radioactive decay curves. https://www.britannica.com/science/decay-constant. 
I have made a small model that simulates a number of `days` where birds start of with a number of caches (`num_cach_start`). 
The number of birds (`num_birds`) can be inputted as well. 

```{r simulating the formulas to test, include=TRUE, message=FALSE, warning=FALSE}
# Number of days to simulate 
days<-90
# Number of caches to start with 
num_cach_start<-100
# How to often do we repeat this, and take an average at the end 
num_birds<-100 
# start for loop   
for (j in 1:num_birds){
  if (j==1){
    repeats_list<-list()}
  # Start loop trough timesteps 
          ts<-days*72
          for (i in 1:ts){
          if (i==1){
            samplesize<-num_cach_start
            number<-1:ts
            df<-as.data.frame(number)}
          df$samplesize[i]<-samplesize
          # Determine the decay constant
          # We take this from an exponential decay curve with a T-halflife of 1440 timesteps
          # This comes down to 20 days, as described in P & L (2001) and Brodin 1994
          # Formula: lambda = 0.693/T-halflife 
          lambda<-(ln(2))/1440
          # Take the sample size into account 
          lambda_2<-lambda*samplesize
          # To find out the probability that k items out of x number of caches have decayed after 1 timestep
          # CAlcualte this probability for different values of k and then sum them up to find the total probability of any number of items decaying 
          # To find out the expected umber of items that decayed, calculated teh mean (lambda) of a poisson distribution 
          # Using complement probability 
          # P(at least one item decays) = 1 - (P (X = 0))
          # With P(X=0) the probability that no items decay 
          # So first calculate the P(X=0) with k= 0 (0 items decayed )
          # P(X=0)= ((e^-lambda) * (lambda^0))/0! = e^(-lambda)
          # We know lambda so we can easily calcualte P(X=0)
          P_noDecay<-exp(-lambda_2)
          df$P_noDecay[i]<-P_noDecay
          # Now calcualte the chance that 1 or more items decayed 
          P_oneOrMore<-(1-P_noDecay)
          df$P_oneOrMore[i]<-P_oneOrMore
          # Pull a random number
          P_random<-runif(1)
          df$random[i]<-P_random
          # Check 
          if(P_oneOrMore>P_random){
            df$singleDecay[i]<-1
            samplesize<-samplesize-1
            # make sure it doesnt go below 0 
            if(samplesize<0){
              samplesize<-0
            }
          }else{
          df$singleDecay[i]<-0 }  }
          df$num_rep<-j
        # Put the dataframe in the list 
          repeats_list[[j]]<-df
} # end the j for loop
# bind together
total_df<-do.call('rbind', repeats_list)
# aggregate means 
mean_df<-total_df%>%
  group_by(number) %>%
  summarise(mean_samplesize=mean(samplesize))
```

The output can be plotted as follows. The green horizontal line shows the starting number of caches. 
Red vertical lines indicate 1 halflife time to be passed (20 days). The top horizontal line indicates half of the initial caches. 
The second horizontal life indicates 1/4 of the initial caches, etc.  <span style="color:red">Check with Tom if he's happy with this.</span> 

```{r plot the simulation output, include=TRUE, warning=FALSE, message=FALSE, echo=FALSE}
# output a plot 
plot(mean_df$number, mean_df$mean_samplesize, ylim=c(0,100), main='Decay of cache number', xlab='Timestep', ylab='Number of caches')
abline(v=1440, col='tomato', lwd=1)
abline(h=num_cach_start, col='forestgreen', lwd=3)
abline(h=(num_cach_start/2), col='tomato', lwd=1)
abline(v=2880, col='tomato', lwd=1)
abline(h=(num_cach_start/4), col='tomato' ,lwd=1)
abline(v=4320, col='tomato', lwd=1)
abline(h=(num_cach_start/8), col='tomato' ,lwd=1)
abline(v=5760, col='tomato', lwd=1)
abline(h=(num_cach_start/16), col='tomato' ,lwd=1)

```

Now I need to build a function that can fit into our larger model and test it. 

```{r build the model function, include=TRUE, warning=FALSE, message=FALSE}
# Half life should be set in the general set up 
cache_halflife<-20*72                             # 15/09/2023: Included in gen setup function 
# Same for lambda 
lambda<-(ln(2))/cache_halflife                    # 15/09/2023: Included in gen setup function 
# The two matrices need to be initiated in the individual setup ( I think, just check where the predation matrices are)
# Here are some dummy ones 
mat_Pdecay<-matrix(NA,1,20)                       # 15/09/2023: Included in indiv-setup function 
decay_count<-matrix(NA, 1,20)                     # 15/09/2023: Included in indiv-setup function 
mat_caches<-matrix(c(NA), 1, 20)
mat_caches[1,1]<-0

# write function 
pilf_func<-function(i,t, lambda){
  # Calculcate the current lambda for all caches that this bird has 
  cur_lambda<<-(lambda*mat_caches[i,t])
  # calculate the probability of no decay at all
  P_noDecay<<-exp(-cur_lambda)
  # Now calculate the chance that 1 or more caches decayed 
  P_oneOrMore<<-(1-P_noDecay)
  # add that to the matrix 
  mat_Pdecay[i,t]<<-P_oneOrMore
  # Set a random nuber
  P_random<<-runif(1)
  
  if(P_oneOrMore>P_random){
    # pilfer 1 item 
    mat_caches[i,t]<<-(mat_caches[i,t]-1)
    if(mat_caches[i,t]<0){
      mat_caches[i,t]<<-0
    }
    # set the counting matrix 
    decay_count[i,t]<<-1
  }else{
    decay_count[i,t]<<-0
  }
}


# To test the function write a little loop around it 

for (k in 1:20){

pilf_func(i=1,t=k, lambda)
  
  if(k==20){
    print('done')
  }else{
  # need to artificially move the cache number to the next timestep
  mat_caches[,(k+1)]<-mat_caches[,k]
  print(paste(k, 'done'))
  }
  
}

```

It looks like the function works well. Now I need to include it in the existing code, with the following steps. 

* set `cache_halflife` and `lambda` in the general setup function 
* initiate the `mat_Pdecay` and `decay_count` matrices in the individual setup function 
* Add the `pilf_func` to the `FuncSource` file
* Plug the `pilf_func` into the models: This should be at the end of each timestep, just before the wrapup 
* Check that the `ts_prep_func` correctly transfers the number of caches to the next timestep 
* Check if `retrieval_func` cannot cause caches to go lower than 0 