---
title: "Compiling level-output from the HPC"
author: "Vera Vinken"
date: "`r Sys.Date()`"
output: html_document
---
  
## Packages 

```{r packages, include=TRUE, message=FALSE, warning=FALSE}

```

## Background
On the HPC I'll run the models for 1 level of the different branches (see `set_combination_branding.Rmd` script). The outcome will be x * 25 files with model outcomes of 1000 individuals over 30 days of one specific model. `X` being the number of unique thresholds (that are relevant) in each level. With this code I will load the data that comes out and take the following steps: 

- Calculate the mean survival across each of the 25 repetitions of each threshold-combination 
- Find the threshold combination with the highest survival 

From there, I can feed this combination into the next level, using the `set_combination_branding.Rmd` script. I can feed in the combination and output a csv file that has all new threshold for the next level. 

This csv file can be saved on the HPC, from which I can then run the next level. 

## Load data 
```{r set working directories}
file_folder<-"C:/Users/c0070955/OneDrive - Newcastle University/1-PHD-project/Modelling/HPC/predesigned_branches"
setwd(file_folder)

```
