---
title: "setCombinationBranch_Branch6_level3"
author: "Vera Vinken"
date: "10/06/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
## Packages 

```{r packages, include=TRUE, message=FALSE, warning=FALSE}
library(dplyr)

library(stringr) # to select the 2nd digit of a number with the str_sub() function 

library(beepr) # beep when done 


library(stringi) # first element from string


# wd sourcefile 
  sourcefile_wd<- "C:/Local_R/BiPhD-ABM/Templates"    

# Load the sourcefiles 
  setwd(sourcefile_wd)
  source('functions_vera.R')


```

## Background

## Basic settings 
```{r settings}
model_type<-432
```

## Set working directories 
```{r set working directories}
l2_result_folder<-"C:/Users/c0070955/OneDrive - Newcastle University/1-PHD-project/Modelling/HPC/predesigned_branches/output_subset2_6/level_2/concat_results/"

general_folder<-"C:/Users/c0070955/OneDrive - Newcastle University/1-PHD-project/Modelling/HPC/predesigned_branches"


```

## Pull the data 

```{r pull the conatanated data from level 2}
# Pull data of most recent concatenation of this model in level 2
HL_df<-grab_recent(wd = l2_result_folder, data_type = paste0("MOD_", model_type, "_lev2.Rda"))


```
## Extract the first row 

Extract the first row of the dataframe so I can get to the "best" thresholds 

```{r extract best ths}
best_th_l2<-HL_df[1,5:10]

```

## Calculate the new minimum and maxima 

For this, I first need to find the stepsize. For the 6 branch in level 3, there will be 6x4x4 = 96 options which need to be spread across the original range of each variable. Which variable this is, will be model specific. I will first create a list with these calculated so this can be referenced. 

```{r create a list with the references for stepsize}
SC_stepsize<-(round(((0.4-0)/96), digits=10))
FR_stepsize<-(round(((4-0)/96), digits=10))
FLR_stepsize<-(round(((0.6-(-0.6))/96), digits=10))


if (model_type==431 |model_type==432 ){
  # proxies are FR and FLR 
  proxy_1<-FR_stepsize
  proxy_2<-FLR_stepsize
}else if(model_type==531 |model_type==532){
  # proxies are SC and FR
  proxy_1<-SC_stepsize
  proxy_2<-FR_stepsize
}else if(model_type==631 |model_type==632){
    # proxies are SC and FLR
  proxy_1<-SC_stepsize
  proxy_2<-FLR_stepsize
  
}else{
  print("Error in model type")
}


```

Now decide on the new 4 branches for each of the variable thresholds 

```{r caluclate new branches for ths}

best_th_l2<-as.data.frame(best_th_l2)

# Calculate the new minimum for th1 
                      new_v1_th1<-c((best_th_l2[1,1]-(1.5*proxy_1)), 
                                    (best_th_l2[1,1]-(0.5*proxy_1)), 
                                    (best_th_l2[1,1]+(0.5*proxy_1)), 
                                    (best_th_l2[1,1]+(1.5*proxy_1)))
                      new_v2_th1<-c((best_th_l2[1,2]-(1.5*proxy_2)), 
                                    (best_th_l2[1,2]-(0.5*proxy_2)), 
                                    (best_th_l2[1,2]+(0.5*proxy_2)), 
                                    (best_th_l2[1,2]+(1.5*proxy_2)))
                      new_v1_th2<-c((best_th_l2[1,3]-(1.5*proxy_1)), 
                                    (best_th_l2[1,3]-(0.5*proxy_1)), 
                                    (best_th_l2[1,3]+(0.5*proxy_1)), 
                                    (best_th_l2[1,3]+(1.5*proxy_1)))
                      new_v2_th2<-c((best_th_l2[1,4]-(1.5*proxy_2)), 
                                    (best_th_l2[1,4]-(0.5*proxy_2)), 
                                    (best_th_l2[1,4]+(0.5*proxy_2)), 
                                    (best_th_l2[1,4]+(1.5*proxy_2)))
                      new_v1_th3<-c((best_th_l2[1,5]-(1.5*proxy_1)), 
                                    (best_th_l2[1,5]-(0.5*proxy_1)), 
                                    (best_th_l2[1,5]+(0.5*proxy_1)), 
                                    (best_th_l2[1,5]+(1.5*proxy_1)))
                      new_v2_th3<-c((best_th_l2[1,6]-(1.5*proxy_2)), 
                                    (best_th_l2[1,6]-(0.5*proxy_2)), 
                                    (best_th_l2[1,6]+(0.5*proxy_2)), 
                                    (best_th_l2[1,6]+(1.5*proxy_2)))
            
                                    
                      


```

## Now create the grid for the new dataframe 


```{r create grid for L3}
 # Create a grid with all the possible combinations of th1 and th 2 
                      grid<-expand.grid(new_v1_th1, 
                                        new_v2_th1, 
                                        new_v1_th2,
                                        new_v2_th2, 
                                        new_v1_th3, 
                                        new_v2_th3)
                      colnames(grid)<-c("v1_th1", "v2_th1", "v1_th2", "v2_th2", "v1_th3", "v2_th3")
                      # Subset this for cases where th2 > th 1 - not really necessary anymore 
                      grid<-grid%>%
                    filter(case_when( ((model_type=="431")|(model_type=="432"))~v1_th1>0 & v1_th2>0 & v1_th3>0, 
                                      ((model_type=="531")|(model_type=="532"))~v1_th1>0 & v2_th1>0 & v1_th2>0 & v2_th2>0 & v1_th3>0 & v2_th3>0,
                                      ((model_type=="631")|(model_type=="632"))~v1_th1>0 & v1_th2>0 & v1_th3>0))%>%
                    filter(v1_th1<v1_th2)%>%
                    filter(v2_th1<v2_th2)%>%
                    filter(v1_th2<v1_th3)%>%
                    filter(v2_th2<v2_th3)
                      
                      
  # And save the dataframe 
    setwd(general_folder)
    write.table(grid, file=paste0('th_HPC_sub2', "_branch6","_x3", "_mod", 
                                            model_type, '_level3', '.csv'), row.names = F, col.names = F)
```