---
title: "Extracting model results"
author: "Vera Vinken"
date: "`r Sys.Date()`"
output: html_document
---
  
 

```{r packages, include=FALSE, message=T, warning=T}

# If Tom (or someone else ) wants to use this on their computer --> any packages that are not installed need to be installed 
    # List of needed packages
    packages_to_install <- c("ggplot2", "gridExtra", "parallel", "dplyr", "purrr", "truncnorm", "data.table", "foreach", "doParallel", "ggpubr", "gridExtra", "pracma", "stringr", "plotly", "hrbrthemes", "tibble")
    # find which packages are needed 
    new_packages <- packages_to_install[!(packages_to_install %in% installed.packages()[ ,"Package"])]
    # install ones that were missing 
    if(length(new_packages)>0){
      install.packages(new_packages)
      }

# Load packages 
  library(ggplot2)
   library(gridExtra)       # grids of ggplots 
  library('parallel')       # for parallel computing
  library('doParallel')     # As above 
  library(dplyr)            # merging dataframes, using mutate etc. 
  library(purrr)            # To use the dataframe mapping functions 
  library(truncnorm)        # creating normal distributions 
  library(data.table)
  library(foreach)
  library(doParallel)
  library(ggpubr)             # To arrange plots 
  library(gridExtra)          # for grid.arrange 
  library(pracma)
  library(stringr)
  library(plotly)
  library(hrbrthemes)
  library(tibble)

```

## Background 

This script should do the following: 

- run each of the models with the optimal values 
- concatenate this all into a big dataframe
- That dataframe should be ready for the shiny. 

## Set working directories & Load sourcefiles 

If this is running from the shared Rproject, this should all be automated. 
```{r set wd and load sourcefiles, include=TRUE, message=FALSE, echo=F, warning=FALSE}
# Set directories 
  # # Where are the sourcefiles located? 
  sourcefile_wd<- "C:/Local_R/BiPhD-ABM/May23"      
  # # Specify the parent folder where you want to save results 
  # #parent_saving_wd<-"C:/Users/c0070955/OneDrive - Newcastle University/1-PHD-project/Modelling/R/Model_output/Post_param_results_October23" 

# Load the sourcefiles 
  setwd(sourcefile_wd)
  source('MOD_1_FuncSource.R')
  source('ModelSource.R')

```


## Comparing model results 

### Specify what data you are interested in 

* `models`: Here you can input which models you want to compare with each other, make sure to put them between `""` and don't include `,` or `.` in the model numbers. E.g. use `11`, `12` and `332`.  If you are just interested in 1 model, this is fine as well. Models x.1 are the non-hoarding models. x.2 are the left-over hoarders. models x.3.1 are direct hoarders that have hoarding as the 'top' behaviour (above highest threshold). Models x.3.2 are direct hoarders that have resting as the 'top' behaviour (above the highest threshold). As a default, this is set to all models, if you want to change this you need to run the code from scratch, which will take more time. 


* `int_var`: Here you specify your variable of interest. These are only relevant for the graphs that are split per enviornment, where you will visualise the chosen variable across the 12 environments 
    * `eat` = proportion of alive birds that are eating at any given timestep. This is eat-only behaviour. Either birds that have 'eating' as a seperate beahviour. Or leftover-hoarding birds that foud a food item to eat, but it is not enough to hoard as well. 
    * `eat_hoard` = proportion of alive birds that are doing the 'eat and hoard leftovers' behaviour at any given timestep. Note that this is only an option for X.2 models. And only in the case that they find enough items so they can hoard something. 
    * `forage` = proportion of alive birds that goes out to forage. Foraging happens before the 'eating' behaviour, before the 'direct hoarding' behaviour and before 'eat_haording' behaviour. 
    * `dir_hoard`= the proportion of alive birds that does the 'direct hoarding' behaviour at any given timestep. Note that only X.3.Y models can do this. 
    * `alive` = The percentage of birds that is alive at any given timestep 
    * `caches` = The number of caches birds have at any give timestep. Note that non-hoarding species do get a starting level of cahches, they just cannot access them. 
    * `find_food` = The number of food items that are found in each step 
    * `fat_res` = The fat reserve of alive birds in each timestep 
    * `stom_con`= The stomach content of alive birds in each timestep 
    * `fat_loss_r` = The fat loss rate of alive birds in each timestep 
    * `mass`= The mass of alive birds in each timestep 
    * `predation` = Average of successful predation attempts in each timestep 
    * `rest` = The proportion of alive birds that is resting in each timestep 
    * `retrieve` = The proportion of alive birds that is retrieving in each timestep. Note this is only possible for hoarding models (X.2 and X.3.Y)
    * `sleep`= The proportion of alive birds that is sleeping in any given timestep 
    * `cache_decay` = The average of decayed caches in every given timestep 
    * `temp` = Temperature in degrees Celcius 
    
* `num_birds`: specify the number of individual birds you want to run each model for (default = 1000). Only change this if you want to run the models from scratch. You also need to change which code chunks are running in that case. 

* `daylight_h`: specify how many daylight hours you want (default = 8). Only change this if you want to run the models from scratch. You also need to change which code chunks are running in that case. 

* `days`: specify how many days you want in your simulation (default = 30). Only change this if you want to run the models from scratch. You also need to change which code chunks are running in that case. 


```{r set which model to run, include=TRUE, warning=FALSE,echo=F, message=FALSE}
models<-c("11", "21", "31", "41", "51", "61",
          "12", "22", "32","42", "52", "62" ,
          "131", "231", "331", "431", "531", "631",
          "132", "232", "332", "432", "532", "632") 

# If you are using the previously generated data, do not change these the code will use teh default settings 
num_birds<-1000
daylight_h<-8
days<-30 
```

### Repeat current settings 
The current run includes the following settings: 

* **Models to be evaluated** = `r models`
* **Variable of interest** (if we are looking at split environments) = `r int_var`
* **Number of birds** = `r num_birds`
* **Daylight hours** = `r daylight_h`
* **Number of days in simulation** = `r days`


Then follows the code that loops through each of the models specified and runs them for 30 days and 1000 individuals. In future, I'll make this flexible at the top as well, but for now it is hard coded. The code is not printed here, but you can look at it in the Rmarkdown file. This is followed by code for the visualization. What is visualized depends on the above input variables. 

```{r loop through models to run, include=F, warning=F, message=F, eval=F}
for (i in 1:length(models)){
  
  if (i==1){
    env_func_out_list<-list()
  }
  
  if (models[i]==11){
    # Code that runs 11
    env_func_1_1_par(days = days, 
                     N= num_birds, 
                     th_forage_sc = 0.002083333, 
                     daylight_h = daylight_h, 
                     modelType = 11) 
  }else if (models[i]==12){
    
    # Code that runs 12 
    env_func_1_2_par(days = days, 
                     N= num_birds, 
                     th_forage_sc1 = 0.02708333, 
                     th_forage_sc2 = 0.08125, 
                     daylight_h = daylight_h, 
                     modelType = 12)
    
  } else if (models[i]==131){
    # Code that runs 131 
      env_func_1_3_1_par(days = days, 
                         N= num_birds, 
                         th_forage_sc1 = 0.03125 , 
                         th_forage_sc2 = 0.08958333, 
                         th_forage_sc3 = 0.29375 , 
                         daylight_h = daylight_h, 
                         modelType = 131)
    
  } else if (models[i]==132){
    # Code that runs 132
        env_func_1_3_2_par(days = days, 
                           N= num_birds, 
                           th_forage_sc1 =0.02708333, 
                           th_forage_sc2 =0.13125, 
                           th_forage_sc3 =0.1354167, 
                           daylight_h = daylight_h, 
                           modelType = 132)
    
  } else if (models[i]==21){
    # Code that runs 21 
    env_func_2_1_par(days = days, 
                     N= num_birds, 
                     th_forage_fr = 1.604167, 
                     daylight_h = daylight_h, 
                     modelType = 21)
    
  } else if (models[i]==22){
    # Code that runs 22 
    env_func_2_2_par(days = days, 
                     N= num_birds, 
                     th_forage_fr1 = 1.020833, 
                     th_forage_fr2 = 1.4375 , 
                     daylight_h = daylight_h, 
                     modelType = 22)
  } else if (models[i]==231){
    
    
    # Code that runs 231 
      env_func_2_3_1_par(days = days, N= num_birds, 
                         th_forage_fr1 = 0.3958333, 
                         th_forage_fr2 =1.395833, 
                         th_forage_fr3 = 2.9375, 
                         daylight_h = daylight_h, 
                         modelType = 231)
  } else if (models[i]==232){
    
    
    # Code that runs 232 
    env_func_2_3_2_par(days = days, 
                       N= num_birds, 
                       th_forage_fr1 = 0.3958333, 
                       th_forage_fr2 = 2.229167, 
                       th_forage_fr3 = 3.8125, 
                       daylight_h = daylight_h, 
                       modelType = 232)
  } else if (models[i]==31){
    
    
    # Code that runs 31 
    env_func_3_1_par(days = days, 
                     N= num_birds, 
                     th_forage_flr = 0.23125, 
                     daylight_h = daylight_h, 
                     modelType = 31)
    
  } else if (models[i]==32){
    
    # Code that runs 32 
    env_func_3_2_par(days = days, 
                     N= num_birds, 
                     th_forage_flr1 = -0.06875, 
                     th_forage_flr2 = 0.11875, 
                     daylight_h = daylight_h, 
                     modelType = 32)
    
  } else if (models[i]==331){
    
    # Code that runs 331 
    env_func_3_3_1_par(days = days, 
                       N= num_birds, 
                       th_forage_flr1 = -0.13125, 
                       th_forage_flr2 = 0.21875, 
                       th_forage_flr3 = 0.41875, 
                       daylight_h = daylight_h, modelType = 331)
    
  } else if (models[i]==332){
    
    # Code that runs 332
    env_func_3_3_2_par(days = days, 
                       N= num_birds, 
                       th_forage_flr1 = -0.11875, 
                       th_forage_flr2 = 0.25625, 
                       th_forage_flr3 = 0.49375, 
                       daylight_h = 8, modelType = 332)
  }else if (models[i]==41){
    
    
    # Code that runs 41 
    env_func_4_1_par(days = days, 
                     N= num_birds, 
                     th_forage_fr = 1.520833, 
                     th_forage_flr = -0.00625, 
                     daylight_h = daylight_h, 
                     modelType = 41)
    
  } else if (models[i]==42){
    
    # Code that runs 42 
    env_func_4_2_par(days = days, 
                     N= num_birds, 
                     th_forage_fr1 = 1.3125,
                     th_forage_flr1 = -0.03125, 
                     th_forage_fr2 = 1.354167,
                     th_forage_flr2 = 0.00625, 
                     daylight_h = daylight_h, 
                     modelType = 42)
    
  } else if (models[i]==431){
    
    # Code that runs 431 
    env_func_4_3_1_par(days = days, 
                       N= num_birds, 
                       th_forage_fr1 = 0,
                       th_forage_flr1 = 0, 
                       th_forage_fr2 = 0,
                       th_forage_flr2 = 0, 
                       th_forage_fr3 = 0,
                       th_forage_flr3 = 0, 
                       daylight_h = daylight_h,
                       modelType = 431)
    
  } else if (models[i]==432){
    
    # Code that runs 432
    env_func_4_3_2_par(days = days, 
                       N= num_birds, 
                       th_forage_fr1 = 0,
                       th_forage_flr1 = 0, 
                       th_forage_fr2 = 0,
                       th_forage_flr2 = 0, 
                       th_forage_fr3 = 0,
                       th_forage_flr3 = 0, 
                       daylight_h = 8, 
                       modelType = 432)
    
  }else if (models[i]==51){
    
    
    # Code that runs 51 
    env_func_5_1_par(days = days, 
                     N= num_birds, 
                     th_forage_sc = 0.03125,
                     th_forage_fr = 0.3125, 
                     daylight_h = daylight_h, 
                     modelType = 51)
    
  } else if (models[i]==52){
    
    # Code that runs 52 
    env_func_5_2_par(days = days, 
                     N= num_birds, 
                     th_forage_sc1 = 0.0645833,
                     th_forage_fr1 = 1.3125,
                     th_forage_sc2 = 0.1145833,
                     th_forage_fr2 = 1.395833,
                     daylight_h = daylight_h, 
                     modelType = 52)
    
  } else if (models[i]==531){
    
    # Code that runs 531 
    env_func_5_3_1_par(days = days, 
                       N= num_birds, 
                       th_forage_sc1 = 0,
                       th_forage_fr1 = 0, 
                       th_forage_sc2 = 0,
                       th_forage_fr2 = 0, 
                       th_forage_sc3 = 0,
                       th_forage_fr3 = 0, 
                       daylight_h = daylight_h,
                       modelType = 531)
    
  } else if (models[i]==532){
    
    # Code that runs 532
    env_func_5_3_2_par(days = days, 
                       N= num_birds, 
                       th_forage_sc1 = 0,
                       th_forage_fr1 = 0, 
                       th_forage_sc2 = 0,
                       th_forage_fr2 = 0, 
                       th_forage_sc3 = 0,
                       th_forage_fr3 = 0, 
                       daylight_h = 8, 
                       modelType = 532)
    
  } else if (models[i]==61){
    
    
    # Code that runs 61 
    env_func_6_1_par(days = days, 
                     N= num_birds, 
                     th_forage_sc = 0.01458333,
                     th_forage_flr = -0.58125, 
                     daylight_h = daylight_h, 
                     modelType = 61)
    
  } else if (models[i]==62){
    
    # Code that runs 62 
    env_func_6_2_par(days = days, 
                     N= num_birds, 
                     th_forage_sc1 = 0.05208333,
                     th_forage_flr1 = -0.20625,
                     th_forage_sc2 = 0.09791667,
                     th_forage_flr2 = -0.18125,
                     daylight_h = daylight_h, 
                     modelType = 62)
    
  } else if (models[i]==631){
    
    # Code that runs 631 
    env_func_6_3_1_par(days = days, 
                       N= num_birds, 
                       th_forage_sc1 = 0,
                       th_forage_flr1 = 0, 
                       th_forage_sc2 = 0,
                       th_forage_flr2 = 0, 
                       th_forage_sc3 = 0,
                       th_forage_flr3 = 0, 
                       daylight_h = daylight_h,
                       modelType = 631)
    
  } else if (models[i]==632){
    
    # Code that runs 632
    env_func_6_3_2_par(days = days, 
                       N= num_birds, 
                       th_forage_sc1 = 0,
                       th_forage_flr1 = 0, 
                       th_forage_sc2 = 0,
                       th_forage_flr2 = 0, 
                       th_forage_sc3 = 0,
                       th_forage_flr3 = 0, 
                       daylight_h = 8, 
                       modelType = 632)
  }
  
  
    # Add the "model" column with value "model type" and the "env" column to each dataframe in the list
    # 
    output_env_func[[2]]<- lapply(seq_along(output_env_func[[2]]), function(j) {
      df <- output_env_func[[2]][[j]]
      df$model <- models[i]
      df$perf_survival <- output_env_func[[1]][[1]]
      df$env <- j
      return(df)
    })
  
  # remove the survival 
  output_env_func<-output_env_func[-1]
  output_env_func<-output_env_func[[1]]
  
  # bind the environments together 
  output_env_func_df<-do.call(rbind, output_env_func)
  
  # Now save the result of this iteration in a meaningful way 
  env_func_out_list[[i]]<-output_env_func_df
  
  print(paste("model done=", models[i]))
  
}

env_func_out_df<-as.data.frame(do.call("rbind", env_func_out_list))
#rm(env_func_out_list)




```

Indicate if the model is a hoarder or non-hoarder 


```{r indicate if hoarder}

df_out<-env_func_out_df%>%
  mutate(hoard = case_when(
          endsWith(model, "11") ~ 0, 
          endsWith(model, "12") ~ 1, 
          endsWith(model, "131") ~ 1, 
          endsWith(model, "132") ~ 1, 
          endsWith(model, "21") ~ 0, 
          endsWith(model, "22") ~ 1, 
          endsWith(model, "231") ~ 1, 
          endsWith(model, "232") ~ 1,
          startsWith(model, "31") ~ 0, 
          startsWith(model, "32") ~ 1, 
          startsWith(model, "331") ~ 1, 
          startsWith(model, "332") ~ 1,
          endsWith(model, "41" )~ 0,
          endsWith(model, "42" )~ 1,
          endsWith(model, "431" )~ 1,
          endsWith(model, "432" )~ 1,
          endsWith(model, "51" )~ 0,
          endsWith(model, "52") ~ 1,
          endsWith(model, "531") ~ 1,
          endsWith(model, "532" )~ 1,
          endsWith(model, "61" )~ 0,
          endsWith(model, "62" )~ 1,
          endsWith(model, "631" )~ 1,
          endsWith(model, "632" )~ 1
    
  )) %>%
 mutate(subset = case_when(
    startsWith(model, "1") ~ 1, 
    startsWith(model, "2") ~ 1, 
    startsWith(model, "3") ~ 1,
    startsWith(model, "4") ~ 2, 
    startsWith(model, "5") ~ 2, 
    startsWith(model, "6") ~ 2,
    TRUE ~ NA_real_  # Default case if none of the above conditions match
  )) %>%
  mutate(hoarding_type = case_when(
          endsWith(model, "11") ~ 1, 
          endsWith(model, "12") ~ 2, 
          endsWith(model, "131") ~ 3, 
          endsWith(model, "132") ~ 4, 
          endsWith(model, "21") ~ 1, 
          endsWith(model, "22") ~ 2, 
          endsWith(model, "231") ~ 3, 
          endsWith(model, "232") ~ 4,
          startsWith(model, "31") ~ 1, 
          startsWith(model, "32") ~ 2, 
          startsWith(model, "331") ~ 3, 
          startsWith(model, "332") ~ 4,
          endsWith(model, "41") ~ 1,
          endsWith(model, "42" )~ 2,
          endsWith(model, "431" )~ 3,
          endsWith(model, "432" )~ 4,
          endsWith(model, "51" )~ 1,
          endsWith(model, "52" )~ 2,
          endsWith(model, "531") ~ 3,
          endsWith(model, "532" )~ 4,
          endsWith(model, "61" )~ 1,
          endsWith(model, "62" )~ 2,
          endsWith(model, "631") ~ 3,
          endsWith(model, "632" )~ 4
  ))%>%
  mutate(proxy = case_when(
              endsWith(model, "11") ~ "SC", 
          endsWith(model, "12") ~ "SC", 
          endsWith(model, "131") ~ "SC", 
          endsWith(model, "132") ~ "SC", 
          endsWith(model, "21") ~ "FR", 
          endsWith(model, "22") ~ "FR", 
          endsWith(model, "231") ~ "FR", 
          endsWith(model, "232") ~ "FR",
          startsWith(model, "31") ~ "FLR", 
          startsWith(model, "32") ~ "FLR", 
          startsWith(model, "331") ~ "FLR", 
          startsWith(model, "332") ~ "FLR",
          endsWith(model, "41" )~ "FR-FLR",
          endsWith(model, "42" )~ "FR-FLR",
          endsWith(model, "431") ~ "FR-FLR",
          endsWith(model, "432" )~ "FR-FLR",
          endsWith(model, "51" )~ "SC-FR",
          endsWith(model, "52") ~ "SC-FR",
          endsWith(model, "531") ~ "SC-FR",
          endsWith(model, "532" )~ "SC-FR",
          endsWith(model, "61" )~ "SC-FLR",
          endsWith(model, "62") ~ "SC-FLR",
          endsWith(model, "631") ~ "SC-FLR",
          endsWith(model, "632" )~ "SC-FLR"
  ))%>%
    mutate(timestep_within_day=timestep%%72)%>%
  mutate(model = as.factor(model))

# Summarise acros the 12 environments 

df_out_Esum<-df_out%>%
  group_by(timestep, id, model)%>%
  summarise(mean_val_env = mean(value, na.rm=T), nObs = n())%>%
  ungroup()

# Summarise across the days 
df_out_Dsum<-df_out%>%
  group_by(id, model, env, timestep_within_day)%>%
  summarise(mean_val_day = mean(value, na.rm=T, nObs = n()))%>%
  ungroup()

# make sure that the lists inside the list have the right name 
setwd(sourcefile_wd)
save(df_out, file="results.Rda")
save(df_out_Esum, file="Esum_results.Rda")
save(df_out_Dsum, file = "Dsum_results.Rda")

```
