---
title: "Extracting model results"
author: "Vera Vinken"
date: "`r Sys.Date()`"
output: html_document
---
  
 

```{r packages, include=FALSE, message=T, warning=T}

# If Tom (or someone else ) wants to use this on their computer --> any packages that are not installed need to be installed 
    # List of needed packages
    packages_to_install <- c("ggplot2", "gridExtra", "parallel", "dplyr", "purrr", "truncnorm", "data.table", "foreach", "doParallel", "ggpubr", "gridExtra", "pracma", "stringr", "plotly", "hrbrthemes", "tibble")
    # find which packages are needed 
    new_packages <- packages_to_install[!(packages_to_install %in% installed.packages()[ ,"Package"])]
    # install ones that were missing 
    if(length(new_packages)>0){
      install.packages(new_packages)
      }

# Load packages 
  library(ggplot2)
   library(gridExtra)       # grids of ggplots 
  library('parallel')       # for parallel computing
  library('doParallel')     # As above 
  library(dplyr)            # merging dataframes, using mutate etc. 
  library(purrr)            # To use the dataframe mapping functions 
  library(truncnorm)        # creating normal distributions 
  library(data.table)
  library(foreach)
  library(doParallel)
  library(ggpubr)             # To arrange plots 
  library(gridExtra)          # for grid.arrange 
  library(pracma)
  library(stringr)
  library(plotly)
  library(hrbrthemes)
  library(tibble)

```

## Background 
With this script, I want to be able to input which models to run and what type of output I want. The rest should be automated and pull from the sorucefiles that I have built my models from. Ideally, I want this to be the file that Tom can use in future, zipped up with all the dependencies so it is very easy to extract data. 


## Set working directories & Load sourcefiles 
If this is running from the shared Rproject, this should all be automated. 
```{r set wd and load sourcefiles, include=TRUE, message=FALSE, echo=F, warning=FALSE}
# Set directories 
  # # Where are the sourcefiles located? 
  sourcefile_wd<- "C:/Local_R/BiPhD-ABM/May23"      
  # # Specify the parent folder where you want to save results 
  # #parent_saving_wd<-"C:/Users/c0070955/OneDrive - Newcastle University/1-PHD-project/Modelling/R/Model_output/Post_param_results_October23" 

# Load the sourcefiles 
  setwd(sourcefile_wd)
  source('MOD_1_FuncSource.R')
  source('ModelSource.R')

```


## Comparing model results 

### Specify what data you are interested in 

* `models`: Here you can input which models you want to compare with each other, make sure to put them between `""` and don't include `,` or `.` in the model numbers. E.g. use `11`, `12` and `332`.  If you are just interested in 1 model, this is fine as well. Models x.1 are the non-hoarding models. x.2 are the left-over hoarders. models x.3.1 are direct hoarders that have hoarding as the 'top' behaviour (above highest threshold). Models x.3.2 are direct hoarders that have resting as the 'top' behaviour (above the highest threshold). As a default, this is set to all models, if you want to change this you need to run the code from scratch, which will take more time. 


* `int_var`: Here you specify your variable of interest. These are only relevant for the graphs that are split per enviornment, where you will visualise the chosen variable across the 12 environments 
    * `eat` = proportion of alive birds that are eating at any given timestep. This is eat-only behaviour. Either birds that have 'eating' as a seperate beahviour. Or leftover-hoarding birds that foud a food item to eat, but it is not enough to hoard as well. 
    * `eat_hoard` = proportion of alive birds that are doing the 'eat and hoard leftovers' behaviour at any given timestep. Note that this is only an option for X.2 models. And only in the case that they find enough items so they can hoard something. 
    * `forage` = proportion of alive birds that goes out to forage. Foraging happens before the 'eating' behaviour, before the 'direct hoarding' behaviour and before 'eat_haording' behaviour. 
    * `dir_hoard`= the proportion of alive birds that does the 'direct hoarding' behaviour at any given timestep. Note that only X.3.Y models can do this. 
    * `alive` = The percentage of birds that is alive at any given timestep 
    * `caches` = The number of caches birds have at any give timestep. Note that non-hoarding species do get a starting level of cahches, they just cannot access them. 
    * `find_food` = The number of food items that are found in each step 
    * `fat_res` = The fat reserve of alive birds in each timestep 
    * `stom_con`= The stomach content of alive birds in each timestep 
    * `fat_loss_r` = The fat loss rate of alive birds in each timestep 
    * `mass`= The mass of alive birds in each timestep 
    * `predation` = Average of successful predation attempts in each timestep 
    * `rest` = The proportion of alive birds that is resting in each timestep 
    * `retrieve` = The proportion of alive birds that is retrieving in each timestep. Note this is only possible for hoarding models (X.2 and X.3.Y)
    * `sleep`= The proportion of alive birds that is sleeping in any given timestep 
    * `cache_decay` = The average of decayed caches in every given timestep 
    * `temp` = Temperature in degrees Celcius 
    
* `num_birds`: specify the number of individual birds you want to run each model for (default = 1000). Only change this if you want to run the models from scratch. You also need to change which code chunks are running in that case. 

* `daylight_h`: specify how many daylight hours you want (default = 8). Only change this if you want to run the models from scratch. You also need to change which code chunks are running in that case. 

* `days`: specify how many days you want in your simulation (default = 30). Only change this if you want to run the models from scratch. You also need to change which code chunks are running in that case. 


```{r set which model to run, include=TRUE, warning=FALSE,echo=F, message=FALSE}
models<-c("11", "21", "31", "12", "22", "32", "131", "231", "331", "132", "232", "332") # Keep this as is (unless runnig models from scratch)
int_var<-"stom_con"  # This is hte variable you can chagne in order to inspect specific variables! 

# If you are using the previously generated data, do not change these the code will use teh default settings 
num_birds<-1000
daylight_h<-8
days<-30 
```

### Repeat current settings 
The current run includes the following settings: 

* **Models to be evaluated** = `r models`
* **Variable of interest** (if we are looking at split environments) = `r int_var`
* **Number of birds** = `r num_birds`
* **Daylight hours** = `r daylight_h`
* **Number of days in simulation** = `r days`


Then follows the code that loops through each of the models specified and runs them for 30 days and 1000 individuals. In future, I'll make this flexible at the top as well, but for now it is hard coded. The code is not printed here, but you can look at it in the Rmarkdown file. This is followed by code for the visualization. What is visualized depends on the above input variables. 

```{r loop through models to run, include=F, warning=F, message=F, eval=F}
for (i in 1:length(models)){
  
  if (i==1){
    env_func_out_list<-list()
  }
  
  if (models[i]==11){
    # Code that runs 11
    env_func_1_1_par(days = days, N= num_birds, th_forage_sc = 0.008163265, daylight_h = daylight_h, modelType = 11) 
  }else if (models[i]==12){
    # Code that runs 12 
    env_func_1_2_par(days = days, N= num_birds, th_forage_sc1 = 0.0244898, th_forage_sc2 = 0.03265306 , daylight_h = daylight_h, modelType = 12)
  } else if (models[i]==131){
    # Code that runs 131 
      env_func_1_3_1_par(days = days, N= num_birds, th_forage_sc1 = 0.01632653 , th_forage_sc2 = 0.03265306, th_forage_sc3 = 0.3591837 , daylight_h = daylight_h, modelType = 131)
  } else if (models[i]==132){
    # Code that runs 132
        env_func_1_3_2_par(days = days, N= num_birds, th_forage_sc1 =0.008163265, th_forage_sc2 =0.01632653, th_forage_sc3 =0.03265306, daylight_h = daylight_h, modelType = 132)
  } else if (models[i]==21){
    # Code that runs 21 
    env_func_2_1_par(days = days, N= num_birds, th_forage_fr = 1.714286, daylight_h = daylight_h, modelType = 21)
  } else if (models[i]==22){
    # Code that runs 22 
    env_func_2_2_par(days = days, N= num_birds, th_forage_fr1 = 0.6530612, th_forage_fr2 = 1.142857 , daylight_h = daylight_h, modelType = 22)
  } else if (models[i]==231){
    # Code that runs 231 
      env_func_2_3_1_par(days = days, N= num_birds, th_forage_fr1 = 0.5714286, th_forage_fr2 =1.306122 , th_forage_fr3 = 1.877551 , daylight_h = daylight_h, modelType = 231)
  } else if (models[i]==232){
    # Code that runs 232 
    env_func_2_3_2_par(days = days, N= num_birds, th_forage_fr1 = 0.5714286, th_forage_fr2 = 1.22449, th_forage_fr3 = 1.306122, daylight_h = daylight_h, modelType = 232)
  } else if (models[i]==31){
    # Code that runs 31 
    env_func_3_1_par(days = days, N= num_birds, th_forage_flr = 0.2326531, daylight_h = daylight_h, modelType = 31)
  } else if (models[i]==32){
    # Code that runs 32 
    env_func_3_2_par(days = days, N= num_birds, th_forage_flr1 = -0.06122449, th_forage_flr2 = 0.2081633, daylight_h = daylight_h, modelType = 32)
  } else if (models[i]==331){
    # Code that runs 331 
    env_func_3_3_1_par(days = days, N= num_birds, th_forage_flr1 = -0.1346939, th_forage_flr2 = 0.2081633, th_forage_flr3 = 0.3795918, daylight_h = daylight_h, modelType = 331)
    
  } else if (models[i]==332){
    env_func_3_3_2_par(days = days, N= num_birds, th_forage_flr1 = -0.1346939, th_forage_flr2 = 0.2326531, th_forage_flr3 = 0.2571429, daylight_h = 8, modelType = 332)
  }
  
  output_env_func[[3]]<-models[i]
  
  # Now save the result of this iteration in a meaningful way 
  env_func_out_list[[i]]<-output_env_func
  
  print(paste("model done=", models[i]))
  
}

# make sure that the lists inside the list have the right name 
names(env_func_out_list)<-models
# setwd(sourcefile_wd)
# save(env_func_out_list, file="results.Rda")

```

```{r pull existing results, include=T, warning=F, message=F, eval=T}
setwd("C:/Local_R/BiPHD-ABM/")
load( "results.Rda" )
```


```{r prepare df for limits in graphs, include=F, warning=F, error=F}
# Create the dataframe with the limits for all variables 
int_var_names<-c("eat", "eat_hoard", "forage", "dir_hoard", "alive", "caches", "find_food", "fat_res", "stom_con", "fat_loss_r", "mass", "predation", "rest", "retrieve", "sleep", "cache_decay", "temp")
min<-c(0, 0, 0, 0, 0, 0, 0, 0, 0, -0.65, 0, 0, 0, 0, 0, 0, -15)
max<-c(1, 1, 1, 1, 1, 100, 1, 4.1, 0.45, 0.65, 15, 1, 1, 1, 1, 3, 15)
lim_df<-as.data.frame(cbind(int_var_names, min, max))

# Create dataframe with current variable of interest 
int_var_df<-as.data.frame(int_var)
colnames(int_var_df)<-c("int_var_names")

# Select the relevant row for future using 
lim_df_int<-lim_df%>%
  right_join(int_var_df, by="int_var_names")

# Determine the colour list 
all_models<-c("11", "12", "131", "132", "21", "22", "231", "232", "31", "32", "331", "332")
all_colours<-c("#000000", "#3636A2", "#1094D6", "#5656FF", "#882255", "#FF685D", "#CC6677", "#FFBAB5", "#91CC60",  "#A7B398", "#9BA042", "#E2CA26")
colours_hoard_foc<-c("#797979", "#167D4D", "#FFCE67", "#DC7A89", "#000000", "#51BF66", "#DED191", "#882255", "#D6D6D6", "#79A793", "#CC9B35", "#AA4499" )
colours_prox_foc<-c("#167D4D", "#83B35B", "#08A6DA", "#022586", "#FFCE67",  "#CC9B35", "#FFB166", "#A48C12", "#882255", "#AA4499", "#D08C96", "#FF3F5C" )
# add linteype as well
linetype<-c(1, 2, 3, 4)
col_df<-as.data.frame(cbind(all_models, all_colours, colours_hoard_foc, colours_prox_foc, linetype))

# Now select the relevant ones 
mod_df<-as.data.frame(models)
colnames(mod_df)<-c("all_models")

# no wuse joining to selec thtem from the colour dataframe 
lim_col_df<-col_df%>%
  right_join(mod_df, by="all_models")

# change the names for clarity 
# models<-c("1.1: SC-Non H", "1.2: SC-left H", "1.3.1: SC-Dir H-Htop", "1.3.2: SC-Dir H-Rtop", 
#                             "2.1: FR-Non H", "2.2: FR-left H", "2.3.1: FR-Dir H-Htop", "2.3.2: FR-Dir H-Rtop", 
#                             "3.1: FCR-Non H", "3.2: FCR-left H", "3.3.1: FCR-Dir H-Htop", "3.3.2: FCR-Dir H-Rtop")
# names(env_func_out_list)<-c("1.1: SC-Non H", "1.2: SC-left H", "1.3.1: SC-Dir H-Htop", "1.3.2: SC-Dir H-Rtop", 
#                             "2.1: FR-Non H", "2.2: FR-left H", "2.3.1: FR-Dir H-Htop", "2.3.2: FR-Dir H-Rtop", 
#                             "3.1: FCR-Non H", "3.2: FCR-left H", "3.3.1: FCR-Dir H-Htop", "3.3.2: FCR-Dir H-Rtop")

```


### Survival across the selected models 
The following graph shows how the different models survive across the environments. Survival is hte proportion of birds alive at any given timestep. 

#### Mean across all environments: 
```{r visualise  mean data wrange, include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=5}

focus<-"all_colours"
 # loop through each of the models 
  for (i in 1:length(models)){
    if (i==1){
      output_per_model_list<-list()
    }
    # Set the current model from the env_func_out_list (input to this function)
      cur_out<-env_func_out_list[[models[i]]]
    
      # create empty list
      cur_mod_df<-list()
      
      # Concatenate the dataframes in the list 
      for (df in cur_out[[2]]){
        cur_mod_df<-rbind(cur_mod_df, df)
      }
      # summarize them by variable and timestep 
      cur_mod_df_sum<-cur_mod_df%>%
        group_by(timestep, id)%>%
        summarise(mean_val = mean(value, na.rm=T))%>%
        mutate(mod_id=models[i])%>%
        mutate(line_id=lim_col_df[lim_col_df$all_models==models[i], 5])%>%
        mutate(leg_name=case_when(
          endsWith(mod_id, "11") ~ "1.1: SC-non H", 
          endsWith(mod_id, "12") ~ "1.2: SC-left H", 
          endsWith(mod_id, "131") ~ "1.3.1: SC-dir Htop", 
          endsWith(mod_id, "132") ~ "1.3.2: SC-dir Rtop", 
          endsWith(mod_id, "21") ~ "2.1: FR-non H", 
          endsWith(mod_id, "22") ~ "2.2: FR-left H", 
          endsWith(mod_id, "231") ~ "2.3.1: FR-dir Htop", 
          endsWith(mod_id, "232") ~ "2.3.2: FR-dir Rtop",
          startsWith(mod_id, "31") ~ "3.1: FCR-non H", 
          startsWith(mod_id, "32") ~ "3.2: FCR-left H", 
          startsWith(mod_id, "331") ~ "3.3.1: FCR-dir Htop", 
          startsWith(mod_id, "332") ~ "3.3.2: FCR-dir Rtop",
        ))

      output_per_model_list[[i]]<-cur_mod_df_sum
  }
  
  mean_var_per_model_total<-bind_rows(output_per_model_list)
  
  if(focus=="colours_hoard_foc"){
    colours<-lim_col_df$colours_hoard_foc
  }else if(focus=="colours_prox_foc"){
    colours<-lim_col_df$colours_prox_foc
  }else if(focus=="all_colours"){
    colours<-lim_col_df$all_colours
  }
  
  
```

```{r visualise  mean graph, include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=5}

  plot_var<-ggplot(mean_var_per_model_total[mean_var_per_model_total$id=="alive",], aes(x=timestep, y=mean_val))+
    geom_line(aes( col=leg_name, linetype=line_id))+
    #ggtitle(label=paste("Survival  - Average across 12 env. " ))+
    theme(plot.title=element_text(face='bold'), 
          axis.title.x = element_text(face='bold' ), 
          axis.title.y=element_text(face='bold'), 
          strip.text=element_text(), 
          legend.text=element_text())+
    ylim(c(0,1))+
    scale_color_manual(values=colours)+
    ylab(label="Proportion birds alive")
 
  plot_var<-ggplotly(plot_var)
  plot_var%>% layout(legend = list(title=list(text='<b>Model ID<b>')))

```

#### Split by enevironment 
```{r visualise the outcome survival data wrangle  , include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13}
# legend<-c("1.1: SC-Non H", "1.2: SC-left H", "1.3.1: SC-Dir H-Htop", "1.3.2: SC-Dir H-Rtop",
#                             "2.1: FR-Non H", "2.2: FR-left H", "2.3.1: FR-Dir H-Htop", "2.3.2: FR-Dir H-Rtop",
#                             "3.1: FCR-Non H", "3.2: FCR-left H", "3.3.1: FCR-Dir H-Htop", "3.3.2: FCR-Dir H-Rtop")
int_var<-"alive"
# First determine if you wanted the output split by environment or not 
# I think it makes sense to always print the survival (as you will alwasy be interested in this)
  # plot_env_12_comp_func(env_func_out_list = env_func_out_list, models = models, int_var = "alive", focus="all_colours")
focus="all_colours"
# Loop through the models to extract the correct variable 
  for (i in 1:length(models)){
    if (i==1){
      output_per_model_list<-list()
    }
    # Set the current model from the env_func_out_list (input to this function)
    cur_out<-env_func_out_list[[models[i]]]
    # Now subset for the variable of interest 
    cur_out_filtered<-lapply(cur_out[[2]], function(df){subset(df, id==paste(int_var))})
    # Add the environment number to the dataframes 
    for (j in 1:length(cur_out_filtered)){
      cur_out_filtered[[j]]$env_id<-j
      cur_out_filtered[[j]]$mod_id<-models[i]
      cur_out_filtered[[j]]$line_id<-lim_col_df[lim_col_df$all_models==models[i], 5]
      cur_out_filtered[[j]]<-cur_out_filtered[[j]]%>%
        mutate(leg_name=case_when(
          endsWith(mod_id, "11") ~ "1.1: SC-non H", 
          endsWith(mod_id, "12") ~ "1.2: SC-left H", 
          endsWith(mod_id, "131") ~ "1.3.1: SC-dir Htop", 
          endsWith(mod_id, "132") ~ "1.3.2: SC-dir Rtop", 
          endsWith(mod_id, "21") ~ "2.1: FR-non H", 
          endsWith(mod_id, "22") ~ "2.2: FR-left H", 
          endsWith(mod_id, "231") ~ "2.3.1: FR-dir Htop", 
          endsWith(mod_id, "232") ~ "2.3.2: FR-dir Rtop",
          startsWith(mod_id, "31") ~ "3.1: FCR-non H", 
          startsWith(mod_id, "32") ~ "3.2: FCR-left H", 
          startsWith(mod_id, "331") ~ "3.3.1: FCR-dir Htop", 
          startsWith(mod_id, "332") ~ "3.3.2: FCR-dir Rtop",
        ))%>%
        mutate(temp=if_else((.$env_id=="1"|.$env_id=="3"|.$env_id=="5"|.$env_id=="7"|.$env_id=="9"|.$env_id=="11"), "low", "high"))%>%
        mutate(food_ab=case_when(
          env_id<5 ~ "low", 
          env_id>4 & env_id<9 ~ "medium", 
          env_id>8 ~ "high"
        ))%>%
        mutate(food_pred=if_else((.$env_id=="1"|.$env_id=="2"|.$env_id=="5"|.$env_id=="6"|.$env_id=="9"|.$env_id=="10"), "poisson", "bonanza"))
    }
    output_per_model_list[[i]]<-cur_out_filtered
    
  }
  # for the individual dataframes 
  total_all_models_surv<-list()
  # loop through each of the models  and retrieve all 12 dataframes to put in the 'individual dataframe list' 
  for (sublist in output_per_model_list) {
    for (df in sublist) {
      total_all_models_surv <- rbind(total_all_models_surv, df)
    }
  }

  
  # Now you want to produce a grid of plots, where data is split per environment 
    # On your x-axis you want time "timestep" 
    # On you y-axis you want the value of the chosen variable 'value' 
  
  # select colours
  if(focus=="colours_hoard_foc"){
    colours<-lim_col_df$colours_hoard_foc
  }else if(focus=="colours_prox_foc"){
    colours<-lim_col_df$colours_prox_foc
  }else if(focus=="all_colours"){
    colours<-lim_col_df$all_colours
  }
  
```

```{r visualise the outcome survival graph  , include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13}

  
      plot_12<-ggplot(total_all_models_surv, aes(x=timestep, y=value))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~env_id,  nrow=6)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        labs(fill=" ")

      plot_12<-ggplotly(plot_12)
      plot_12%>% layout(legend = list(title=list(text='<b>Model ID<b>')))
      #plot_12
```

#### Effects of temperature 

```{r compare temperatures, include=T, message=F, warning=F, echo=F}

# add the temp info and regroup 
temp_average_all<-total_all_models_surv%>%
  group_by(timestep,leg_name, temp, line_id, id)%>%
  summarise(mean_val = mean(value, na.rm=T))

```


```{r compare temperatures graph , include=T, message=F, warning=F, echo=F}
facet_order<-c("low", "high")
temp_average_all$temp <- factor(temp_average_all$temp, levels = facet_order)

plot<-ggplot(temp_average_all[temp_average_all$id=="alive",], aes(x=timestep, y=mean_val))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~temp, nrow=2)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        ylab(label="Proportion of birds alive")

      plot<-ggplotly(plot)
plot %>% layout(legend=list(title=list(text='<b> Model ID</b>')))

```


#### Effects of Food abundancy 

```{r compare food abundancy, include=T, message=F, warning=F, echo=F}

# add the temp info and regroup 
food_ab_average_all<-total_all_models_surv%>%
  group_by(timestep,leg_name, food_ab, line_id)%>%
  summarise(mean_val = mean(value, na.rm=T))

```


```{r compare food abundancy graph , include=T, message=F, warning=F, echo=F}
facet_order<-c("low", "medium", "high")
food_ab_average_all$food_ab <- factor(food_ab_average_all$food_ab, levels = facet_order)

plot<-ggplot(food_ab_average_all, aes(x=timestep, y=mean_val))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~food_ab, nrow=3)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        ylab(label="Proportion of birds alive")

      plot<-ggplotly(plot)
plot %>% layout(legend=list(title=list(text='<b> Model ID</b>')))

```


#### Effects of Food predictability

```{r compare food predictability, include=T, message=F, warning=F, echo=F}

# add the temp info and regroup 
food_pred_average_all<-total_all_models_surv%>%
  group_by(timestep,leg_name, food_pred, line_id)%>%
  summarise(mean_val = mean(value, na.rm=T))

```

```{r compare food predictability  graph , include=T, message=F, warning=F, echo=F}
facet_order<-c("poisson", "bonanza")
food_pred_average_all$food_pred <- factor(food_pred_average_all$food_pred, levels = facet_order)

plot<-ggplot(food_pred_average_all, aes(x=timestep, y=mean_val))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~food_pred,nrow=2)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        ylab(label="Proportion of birds alive")

      plot<-ggplotly(plot)
plot %>% layout(legend=list(title=list(text='<b> Model ID</b>')))

```

### Energy proxies 
```{r aggregate for daily patterns, include=TRUE, message=F, warning=F, echo=F,fig.width=17, fig.height=8}
# Input here will be the env_func_out_list 

for (i in 1:length(models)){
  
  if (i==1){
    agg_list<-list()
  }
  # Select hte current list with the 12 dataframes 
  cur_mod<-env_func_out_list[[models[i]]][[2]]
  
  # Cut off the first 3 days 
  
  # add the env row 
  for (j in 1:length(cur_mod)){
    cur_mod[[j]]<-cur_mod[[j]]%>%filter(timestep>216)
    cur_mod[[j]]$env_id<-j
  }
  # bind it all together 
  cur_mod<-bind_rows(cur_mod)
  # add the timestep within day 
  cur_mod<-cur_mod%>%
    mutate(timestep_within_day=timestep%%72)
    #mutate(timestep_within_day = replace(timestep_within_day, timestep_within_day == 0, 72))
  
  # Now summarise the dataframe by timestep within day 
  agg_cur_mod<-cur_mod%>%
    group_by(id, env_id, timestep_within_day)%>%
    summarise(mean_value_day=mean(value, na.rm=T)) %>%#, 
             # mean_ts_within_day=mean(timestep_within_day, na.rm=T))%>%
    mutate(mod_id=rep(models[i]))%>%
     mutate(line_id=lim_col_df[lim_col_df$all_models==models[i], 5])
  
  # Now add to list
  agg_list[[i]]<-agg_cur_mod
}

# bind them all together in a dataframe 
agg_day_df<-bind_rows(agg_list)

```

#### Average over all 12 environments 

```{r check mean across environment for all values, include=TRUE, message=F, warning=F, echo=F}

 # loop through each of the models 
  for (i in 1:length(models)){
    if (i==1){
      mean_vars_day_pat_list<-list()
    }
    # Set the current model from the env_func_out_list (input to this function)
      cur_out<-agg_list[[i]]
      
    # Do the transformations so we get means across all environments 
      cur_mean_out<-cur_out%>%
        group_by(id, timestep_within_day, mod_id)%>%
        summarise(mean_new=mean(mean_value_day, na.rm=T))%>%
         mutate(line_id=lim_col_df[lim_col_df$all_models==models[i], 5])%>%
      mutate(leg_name=case_when(
          endsWith(mod_id, "11") ~ "1.1: SC-non H", 
          endsWith(mod_id, "12") ~ "1.2: SC-left H", 
          endsWith(mod_id, "131") ~ "1.3.1: SC-dir Htop", 
          endsWith(mod_id, "132") ~ "1.3.2: SC-dir Rtop", 
          endsWith(mod_id, "21") ~ "2.1: FR-non H", 
          endsWith(mod_id, "22") ~ "2.2: FR-left H", 
          endsWith(mod_id, "231") ~ "2.3.1: FR-dir Htop", 
          endsWith(mod_id, "232") ~ "2.3.2: FR-dir Rtop",
          startsWith(mod_id, "31") ~ "3.1: FCR-non H", 
          startsWith(mod_id, "32") ~ "3.2: FCR-left H", 
          startsWith(mod_id, "331") ~ "3.3.1: FCR-dir Htop", 
          startsWith(mod_id, "332") ~ "3.3.2: FCR-dir Rtop",
        ))%>%
        mutate(id_beh_label=id)%>%
        mutate(across(id_beh_label, str_replace, "dir_hoard", "hoard"))%>%
         mutate(across(id_beh_label, str_replace, "eat_hoard", "hoard"))

    # Add to list 
      mean_vars_day_pat_list[[i]]<-cur_mean_out
  }
  
  all_vars_day_pat_tot<-bind_rows(mean_vars_day_pat_list)
  


```

```{r plot all variables across enviornments in daily patterns, include=T, echo=F, warning=F, message=F, fig.width=11, fig.height=7}

plot<-ggplot(all_vars_day_pat_tot[all_vars_day_pat_tot$id=="stom_con"|all_vars_day_pat_tot$id=="fat_res"|all_vars_day_pat_tot$id=="fat_loss_r", ], aes(x=timestep_within_day, y=mean_new))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~id, scales='free_y',nrow=6)+
        coord_cartesian(xlim=c(0, 25))+
        #ggtitle(label="Energy proxies- Daily patterns - Across all environments")+
        labs(y="SC  -  FR  -  FCR (in gram or gram/2 hours)", x="Timestep within the Day", col="Model ID")+
        theme(plot.title=element_text( face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text( face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title = element_text(face='bold'))+
  scale_color_manual(values=colours)+
  labs(fill=" ")


p<-ggplotly(plot)
p%>% layout(legend = list(title=list(text='<b>Model ID<b>')))

```


#### Stomach content 

```{r check mean across environment for all values, include=TRUE, message=F, warning=F, echo=F}

 # loop through each of the models 
  for (i in 1:length(models)){
    if (i==1){
      day_pat_per_envlist<-list()
    }
    # Set the current model from the env_func_out_list (input to this function)
      cur_out<-agg_list[[i]]
      
    # Do the transformations so we get means across all environments 
      cur_mean_out<-cur_out%>%
        group_by(id, timestep_within_day, mod_id, env_id,)%>%
        summarise(mean_new=mean(mean_value_day, na.rm=T))%>%
        mutate(line_id=lim_col_df[lim_col_df$all_models==models[i], 5])%>%
      mutate(leg_name=case_when(
          endsWith(mod_id, "11") ~ "1.1: SC-non H", 
          endsWith(mod_id, "12") ~ "1.2: SC-left H", 
          endsWith(mod_id, "131") ~ "1.3.1: SC-dir Htop", 
          endsWith(mod_id, "132") ~ "1.3.2: SC-dir Rtop", 
          endsWith(mod_id, "21") ~ "2.1: FR-non H", 
          endsWith(mod_id, "22") ~ "2.2: FR-left H", 
          endsWith(mod_id, "231") ~ "2.3.1: FR-dir Htop", 
          endsWith(mod_id, "232") ~ "2.3.2: FR-dir Rtop",
          startsWith(mod_id, "31") ~ "3.1: FCR-non H", 
          startsWith(mod_id, "32") ~ "3.2: FCR-left H", 
          startsWith(mod_id, "331") ~ "3.3.1: FCR-dir Htop", 
          startsWith(mod_id, "332") ~ "3.3.2: FCR-dir Rtop",
        ))
      
    # Add to list 
      day_pat_per_envlist[[i]]<-cur_mean_out
  }
  
  day_pat_per_env_df<-bind_rows(day_pat_per_envlist)
  
```


```{r visualise the outcome sc graph  , include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13}

plot<-ggplot(day_pat_per_env_df[day_pat_per_env_df$id=="fat_res",], aes(x=timestep_within_day, y=mean_new))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~env_id,  nrow=6)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        #coord_cartesian(xlim=c(0, 25))+
        labs(fill=" ")

      plot<-ggplotly(plot)
      plot%>% layout(legend = list(title=list(text='Model ID')))
      #plot_12
```

```{r visualise the outcome sc graph  , include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13}
env<-"4"
#x<-day_pat_per_env_df[day_pat_per_env_df$id=="stom_con" & day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="fat_res"& day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="fat_loss_r"& day_pat_per_env_df$env_id==env,]


plot_specificEnv<-ggplot(day_pat_per_env_df[day_pat_per_env_df$id=="stom_con" & day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="fat_res"& day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="fat_loss_r"& day_pat_per_env_df$env_id==env,], aes(x=timestep_within_day, y=mean_new))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~id, scales='free_y', nrow=6)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        coord_cartesian(xlim=c(0, 25))+
        labs(fill=" ")+
        ylab(label="Energy proxy in gram or gram/2 hour")+
        xlab(label="Timestep in day")

      plot_specificEnv<-ggplotly(plot_specificEnv)
      plot_specificEnv%>% layout(legend = list(title=list(text='<b>Model ID<b>')))
      #plot_12
```



```{r visualise the outcome sc graph behaviours  , include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13}
env<-"3"
#x<-day_pat_per_env_df[day_pat_per_env_df$id=="stom_con" & day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="fat_res"& day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="fat_loss_r"& day_pat_per_env_df$env_id==env,]


plot_specificEnv<-ggplot(day_pat_per_env_df[day_pat_per_env_df$id=="rest" & day_pat_per_env_df$env_id==env|day_pat_per_env_df$id=="forage"& day_pat_per_env_df$env_id==env,], aes(x=timestep_within_day, y=mean_new))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~id, scales='free_y', nrow=6)+
        #ggtitle(label=paste(int_var, "- Variable per environment type" ))+
        theme(plot.title=element_text(face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text(face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title=element_blank())+
        scale_color_manual(values=colours)+
        coord_cartesian(xlim=c(0, 25))+
        labs(fill=" ")+
        ylab(label="Energy proxy in gram or gram/2 hour")+
        xlab(label="Timestep in day")

      plot_specificEnv<-ggplotly(plot_specificEnv)
      plot_specificEnv%>% layout(legend = list(title=list(text='<b>Model ID<b>')))
      #plot_12
```









### BEHAVIOURS 

```{r plot all variables across enviornments in daily patterns BHES , include=T, echo=F, warning=F, message=F, fig.width=11, fig.height=7}
# subset the data 

subset<-all_vars_day_pat_tot[all_vars_day_pat_tot$id_beh_label=="rest"|all_vars_day_pat_tot$id_beh_label=="hoard"|all_vars_day_pat_tot$id_beh_label=="eat"|all_vars_day_pat_tot$id_beh_label=="retrieve", ]
# take out the dir_hoarding for leftover hoarders and teh leftover hoarding for direct hoarders (otherwise the graphs go double because dir-hoarders will have 0 for leftover hoarding in each timestep, etc.)
subset<-subset%>%
  filter(!(line_id=="2" & id=="dir_hoard"))%>%
  filter(!(line_id=="3" & id=="eat_hoard"))%>%
  filter(!(line_id=="4" & id=="eat_hoard"))


plot<-ggplot(subset, aes(x=timestep_within_day, y=mean_new))+
        geom_line(aes( col=leg_name, linetype=line_id))+
        facet_wrap(.~id_beh_label, scales='free_y',nrow=2)+
        coord_cartesian(xlim=c(0, 25))+
        #ggtitle(label="Energy proxies- Daily patterns - Across all environments")+
        labs(y="SC  -  FR  -  FCR (in gram or gram/2 hours)", x="Timestep within the Day", col="Model ID")+
        theme(plot.title=element_text( face='bold'), 
              axis.title.x = element_text( face='bold' ), 
              axis.title.y=element_text( face='bold'), 
              strip.text=element_text(), 
              legend.text=element_text(), 
              legend.title = element_text(face='bold'))+
  scale_color_manual(values=colours)+
  labs(fill=" ")


p<-ggplotly(plot)
p%>% layout(legend = list(title=list(text='<b>Model ID<b>')))

```
















<!-- ```{r compare temperatures per sc graph , include=T, message=F, warning=F, echo=F} -->
<!-- agg_day_df<-agg_day_df%>%mutate(food_ab=case_when( -->
<!--           env_id<5 ~ "low",  -->
<!--           env_id>4 & env_id<9 ~ "medium",  -->
<!--           env_id>8 ~ "high" -->
<!--         ))%>% -->
<!--   mutate(temp_env=case_when( -->
<!--     env_id==1 ~ "low",  -->
<!--     env_id==2 ~ "high",  -->
<!--     env_id==3 ~ "low",  -->
<!--     env_id==4 ~ "high",  -->
<!--     env_id==5 ~ "low",  -->
<!--     env_id==6 ~ "high", -->
<!--     env_id==7 ~ "low",  -->
<!--     env_id==8 ~ "high",  -->
<!--     env_id==9 ~ "low",  -->
<!--     env_id==10 ~ "high",  -->
<!--     env_id==11 ~ "low",  -->
<!--     env_id==12 ~ "high",  -->
<!--   )) -->






<!--   mutate(temperature=if_else((.$env_id=="1"|.$env_id=="3"|.$env_id=="5"|.$env_id=="7"|.$env_id=="9"|.$env_id=="11"), "low", "high")) -->
<!-- # -->



<!-- #%>% -->
<!--         %>% -->
<!--         mutate(food_pred=if_else((.$env_id=="1"|.$env_id=="2"|.$env_id=="5"|.$env_id=="6"|.$env_id=="9"|.$env_id=="10"), "poisson", "bonanza")) -->




<!-- int_var<-"stom_con" -->
<!-- # First determine if you wanted the output split by environment or not  -->
<!-- # I think it makes sense to always print the survival (as you will alwasy be interested in this) -->
<!--   # plot_env_12_comp_func(env_func_out_list = env_func_out_list, models = models, int_var = "alive", focus="all_colours") -->
<!-- focus="all_colours" -->
<!-- # Loop through the models to extract the correct variable  -->
<!--   for (i in 1:length(models)){ -->
<!--     if (i==1){ -->
<!--       output_per_model_list<-list() -->
<!--     } -->
<!--     # Set the current model from the env_func_out_list (input to this function) -->
<!--     cur_out<-env_func_out_list[[models[i]]] -->
<!--     # Now subset for the variable of interest  -->
<!--     cur_out_filtered<-lapply(cur_out[[2]], function(df){subset(df, id==paste(int_var))}) -->
<!--     # Add the environment number to the dataframes  -->
<!--     for (j in 1:length(cur_out_filtered)){ -->
<!--       cur_out_filtered[[j]]$env_id<-j -->
<!--       cur_out_filtered[[j]]$mod_id<-models[i] -->
<!--       cur_out_filtered[[j]]$line_id<-lim_col_df[lim_col_df$all_models==models[i], 5] -->
<!--       cur_out_filtered[[j]]<-cur_out_filtered[[j]]%>% -->
<!--         mutate(leg_name=case_when( -->
<!--           endsWith(mod_id, "11") ~ "1.1: SC-non H",  -->
<!--           endsWith(mod_id, "12") ~ "1.2: SC-left H",  -->
<!--           endsWith(mod_id, "131") ~ "1.3.1: SC-dir Htop",  -->
<!--           endsWith(mod_id, "132") ~ "1.3.2: SC-dir Rtop",  -->
<!--           endsWith(mod_id, "21") ~ "2.1: FR-non H",  -->
<!--           endsWith(mod_id, "22") ~ "2.2: FR-left H",  -->
<!--           endsWith(mod_id, "231") ~ "2.3.1: FR-dir Htop",  -->
<!--           endsWith(mod_id, "232") ~ "2.3.2: FR-dir Rtop", -->
<!--           startsWith(mod_id, "31") ~ "3.1: FCR-non H",  -->
<!--           startsWith(mod_id, "32") ~ "3.2: FCR-left H",  -->
<!--           startsWith(mod_id, "331") ~ "3.3.1: FCR-dir Htop",  -->
<!--           startsWith(mod_id, "332") ~ "3.3.2: FCR-dir Rtop", -->
<!--         ))%>% -->
<!--         mutate(temp=if_else((.$env_id=="1"|.$env_id=="3"|.$env_id=="5"|.$env_id=="7"|.$env_id=="9"|.$env_id=="11"), "low", "high"))%>% -->
<!--         mutate(food_ab=case_when( -->
<!--           env_id<5 ~ "low",  -->
<!--           env_id>4 & env_id<9 ~ "medium",  -->
<!--           env_id>8 ~ "high" -->
<!--         ))%>% -->
<!--         mutate(food_pred=if_else((.$env_id=="1"|.$env_id=="2"|.$env_id=="5"|.$env_id=="6"|.$env_id=="9"|.$env_id=="10"), "poisson", "bonanza")) -->
<!--     } -->
<!--     output_per_model_list[[i]]<-cur_out_filtered -->

<!--   } -->
<!--   # for the individual dataframes  -->
<!--   total_all_models_sc<-list() -->
<!--   # loop through each of the models  and retrieve all 12 dataframes to put in the 'individual dataframe list'  -->
<!--   for (sublist in output_per_model_list) { -->
<!--     for (df in sublist) { -->
<!--       total_all_models_sc<- rbind(total_all_models_sc, df) -->
<!--     } -->
<!--   } -->


<!--   # Now you want to produce a grid of plots, where data is split per environment  -->
<!--     # On your x-axis you want time "timestep"  -->
<!--     # On you y-axis you want the value of the chosen variable 'value'  -->

<!--   # select colours -->
<!--   if(focus=="colours_hoard_foc"){ -->
<!--     colours<-lim_col_df$colours_hoard_foc -->
<!--   }else if(focus=="colours_prox_foc"){ -->
<!--     colours<-lim_col_df$colours_prox_foc -->
<!--   }else if(focus=="all_colours"){ -->
<!--     colours<-lim_col_df$all_colours -->
<!--   } -->



<!-- # add the temp info and regroup  -->
<!-- temp_average_all<-total_all_models_sc%>% -->
<!--   group_by(timestep,leg_name, temp, line_id, id)%>% -->
<!--   summarise(mean_val = mean(value, na.rm=T)) -->

<!-- facet_order<-c("low", "high") -->
<!-- temp_average_all$temp <- factor(temp_average_all$temp, levels = facet_order) -->

<!-- plot<-ggplot(temp_average_all[temp_average_all$id=="stom_con",], aes(x=timestep, y=mean_val))+ -->
<!--         geom_line(aes( col=leg_name, linetype=line_id))+ -->
<!--         facet_wrap(.~temp, nrow=2)+ -->
<!--         #ggtitle(label=paste(int_var, "- Variable per environment type" ))+ -->
<!--         theme(plot.title=element_text(face='bold'),  -->
<!--               axis.title.x = element_text( face='bold' ),  -->
<!--               axis.title.y=element_text(face='bold'),  -->
<!--               strip.text=element_text(),  -->
<!--               legend.text=element_text(),  -->
<!--               legend.title=element_blank())+ -->
<!--         scale_color_manual(values=colours)+ -->
<!--         ylab(label="Proportion of birds alive") -->

<!--       plot<-ggplotly(plot) -->
<!-- plot %>% layout(legend=list(title=list(text='<b> Model ID</b>'))) -->

<!-- ``` -->













































































<!-- ```{r visualise the outcome sc graph  , include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13} -->


<!--       plot_12<-ggplot(total_all_models[total_all_models$id=="stom_con",], aes(x=timestep, y=value))+ -->
<!--         geom_line(aes( col=leg_name, linetype=line_id))+ -->
<!--         facet_wrap(.~env_id,  nrow=6)+ -->
<!--         #ggtitle(label=paste(int_var, "- Variable per environment type" ))+ -->
<!--         theme(plot.title=element_text(face='bold'),  -->
<!--               axis.title.x = element_text( face='bold' ),  -->
<!--               axis.title.y=element_text(face='bold'),  -->
<!--               strip.text=element_text(),  -->
<!--               legend.text=element_text(),  -->
<!--               legend.title=element_blank())+ -->
<!--         scale_color_manual(values=colours)+ -->
<!--         labs(fill=" ") -->

<!--       plot_12<-ggplotly(plot_12) -->
<!--       plot_12%>% layout(legend = list(title=list(text='Model ID'))) -->
<!--       #plot_12 -->
<!-- ``` -->











































<!-- ```{r visualise  mean sc across all data wrange, include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=5} -->
<!-- int_var<-"stom)_con" -->
<!-- focus<-"all_colours" -->
<!--  # loop through each of the models  -->
<!--   for (i in 1:length(models)){ -->
<!--     if (i==1){ -->
<!--       output_per_model_list<-list() -->
<!--     } -->
<!--     # Set the current model from the env_func_out_list (input to this function) -->
<!--       cur_out<-env_func_out_list[[models[i]]] -->

<!--       # create empty list -->
<!--       cur_mod_df<-list() -->

<!--       # Concatenate the dataframes in the list  -->
<!--       for (df in cur_out[[2]]){ -->
<!--         cur_mod_df<-rbind(cur_mod_df, df) -->
<!--       } -->
<!--       # summarize them by variable and timestep  -->
<!--       cur_mod_df_sum<-cur_mod_df%>% -->
<!--         group_by(timestep, id)%>% -->
<!--         summarise(mean_val = mean(value, na.rm=T))%>% -->
<!--         mutate(mod_id=models[i])%>% -->
<!--         mutate(line_id=lim_col_df[lim_col_df$all_models==models[i], 5]) -->

<!--       output_per_model_list[[i]]<-cur_mod_df_sum -->
<!--   } -->

<!--   mean_var_per_model_total<-bind_rows(output_per_model_list) -->

<!--   if(focus=="colours_hoard_foc"){ -->
<!--     colours<-lim_col_df$colours_hoard_foc -->
<!--   }else if(focus=="colours_prox_foc"){ -->
<!--     colours<-lim_col_df$colours_prox_foc -->
<!--   }else if(focus=="all_colours"){ -->
<!--     colours<-lim_col_df$all_colours -->
<!--   } -->


<!-- ``` -->
<!-- ```{r visualise  mean sc graph, include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=5} -->

<!--   plot<-ggplot(mean_var_per_model_total[mean_var_per_model_total$id=="alive",], aes(x=timestep, y=mean_val))+ -->
<!--     geom_line(aes( col=mod_id, linetype=line_id))+ -->
<!--     #ggtitle(label=paste("SC  - Average across 12 env. " ))+ -->
<!--     theme(plot.title=element_text(face='bold'),  -->
<!--           axis.title.x = element_text(face='bold' ),  -->
<!--           axis.title.y=element_text(face='bold'),  -->
<!--           strip.text=element_text(),  -->
<!--           legend.text=element_text())+ -->
<!--     ylim(c(0,1))+ -->
<!--     scale_color_manual(values=colours)+ -->
<!--     ylab(label="SC in gram") -->

<!--   plot<-ggplotly(plot_var) -->
<!--   plot %>% layout(legend=list(title=list(text='<b> Model ID</b>'))) -->

<!-- ``` -->





<!-- ### Mean variable values across all environments  -->
<!-- This graph shows the average of each ofthe variables on each timestep. These averages are taken across all environments.  -->
<!-- ```{r visualise  mean, include=T, message=F, warning=F, echo=F, fig.width=17, fig.height=15} -->
<!-- plot_mean_12_env_func(env_func_out_list, models, int_var, focus="all_colours") -->

<!-- ``` -->

<!-- ### Variable of interest, split per enviornment -->
<!-- These graphs show the chosen variable of interest (see above) for each of the environments. The averages are taken across all alive birds in the simulation -->
<!-- ```{r visualise split or mean, include=T, message=F, warning=F, echo=F, fig.width=17, fig.height=15} -->

<!--   plot_env_12_comp_func(env_func_out_list = env_func_out_list, models = models, int_var = int_var, focus="all_colours") -->
<!-- ``` -->

<!-- ### Daily patterns  -->
<!-- With this code I want to do the following:  -->

<!-- * Aggregate over daily patterns  -->
<!-- * Omit the first 3 days This does cause some models to not show up, or show up half way. The number of datapoints in each aggregation will also differ due to survival. We need to consider how we want to deal with that.  -->
<!-- * Compare the pattern of fat-loss, SC and FLR  -->


<!-- ```{r plot the daily patterns, include=T, message=F, warning=F, echo=F, fig.width=10, fig.height=13} -->
<!-- focus<-'all_colours' -->
<!-- if(focus=="colours_hoard_foc"){ -->
<!--     colours<-lim_col_df$colours_hoard_foc -->
<!--   }else if(focus=="colours_prox_foc"){ -->
<!--     colours<-lim_col_df$colours_prox_foc -->
<!--   }else if(focus=="all_colours"){ -->
<!--     colours<-lim_col_df$all_colours -->
<!--   } -->


<!-- plot<-ggplot(agg_day_df[agg_day_df$id==int_var,], aes(x=timestep_within_day, y=mean_value_day))+ -->
<!--         geom_line(aes( col=mod_id, linetype=line_id), size=0.75)+ -->
<!--         #ylim(lim_df_int[1,2], lim_df_int[1,3])+ -->
<!--         facet_wrap(.~env_id, nrow=6)+ -->
<!--         coord_cartesian(xlim=c(0, 25))+ -->
<!--         #coord_cartesian(xlim = c(lim_df_int[1,2], lim_df_int[1,3]))+ -->
<!--         ggtitle(label=paste(int_var, "- per environment - Day pattern" ))+ -->
<!--         labs(y=paste(int_var), x="Timestep within the Day", col="Model ID")+ -->
<!--         theme(plot.title=element_text(face='bold'),  -->
<!--               axis.title.x = element_text(face='bold' ),  -->
<!--               axis.title.y=element_text( face='bold'),  -->
<!--               strip.text=element_text(),  -->
<!--               legend.text=element_text(),  -->
<!--               legend.title = element_text( face='bold'))+ -->
<!--     scale_color_manual(values=colours) -->
<!-- plot<-ggplotly(plot) -->
<!-- plot -->

<!-- int_var_df<-agg_day_df[agg_day_df$id==int_var,] -->

<!-- ``` -->


<!-- ```{r check mean across environment for all values, include=TRUE, message=F, warning=F, echo=F} -->

<!--  # loop through each of the models  -->
<!--   for (i in 1:length(models)){ -->
<!--     if (i==1){ -->
<!--       mean_vars_day_pat_list<-list() -->
<!--     } -->
<!--     # Set the current model from the env_func_out_list (input to this function) -->
<!--       cur_out<-agg_list[[i]] -->

<!--     # Do the transformations so we get means across all environments  -->
<!--       cur_mean_out<-cur_out%>% -->
<!--         group_by(id, timestep_within_day, mod_id)%>% -->
<!--         summarise(mean_new=mean(mean_value_day), n=n())%>% -->
<!--          mutate(line_id=lim_col_df[lim_col_df$all_models==models[i], 5]) -->

<!--     # Add to list  -->
<!--       mean_vars_day_pat_list[[i]]<-cur_mean_out -->
<!--   } -->

<!--   all_vars_day_pat_tot<-bind_rows(mean_vars_day_pat_list) -->



<!-- ``` -->

<!-- ```{r plot all variables across enviornments in daily patterns, include=T, echo=F, warning=F, message=F, fig.width=11, fig.height=12} -->

<!-- plot<-ggplot(all_vars_day_pat_tot, aes(x=timestep_within_day, y=mean_new))+ -->
<!--         geom_line(aes( col=mod_id, linetype=line_id))+ -->
<!--         facet_wrap(.~id, scales='free_y',nrow=6)+ -->
<!--         coord_cartesian(xlim=c(0, 25))+ -->
<!--         ggtitle(label="All variables - Daily patterns - Across all environments")+ -->
<!--         labs(y=paste(int_var), x="Timestep within the Day", col="Model ID")+ -->
<!--         theme(plot.title=element_text( face='bold'),  -->
<!--               axis.title.x = element_text( face='bold' ),  -->
<!--               axis.title.y=element_text( face='bold'),  -->
<!--               strip.text=element_text(),  -->
<!--               legend.text=element_text(),  -->
<!--               legend.title = element_text(face='bold'))+ -->
<!--   scale_color_manual(values=colours) -->


<!-- p<-ggplotly(plot) -->
<!-- p -->

<!-- ``` -->

<!-- ```{r aggregate for daily patterns 3 day graph, include=TRUE, message=F, warning=F, echo=F,fig.width=17} -->
<!-- # Input here will be the env_func_out_list  -->

<!-- for (i in 1:length(models)){ -->

<!--   if (i==1){ -->
<!--     pattern_list<-list() -->
<!--   } -->
<!--   # Select hte current list with the 12 dataframes  -->
<!--   cur_mod<-env_func_out_list[[models[i]]][[2]] -->

<!--   # Cut off the first 3 days  -->

<!--   # add the env row  -->
<!--   for (j in 1:length(cur_mod)){ -->
<!--     cur_mod[[j]]$env_id<-j -->
<!--   } -->
<!--   # bind it all together  -->
<!--   cur_mod<-bind_rows(cur_mod) -->
<!--   day_in_sim<-rep(c(1:days), each=72) -->
<!--   day_in_sim<-rep(day_in_sim, times=204) -->
<!--   # add the timestep within day  -->
<!--   cur_mod<-cur_mod%>% -->
<!--     mutate(timestep_within_day=timestep%%72)%>% -->
<!--     mutate(day_within_sim=day_in_sim)%>% -->
<!--     mutate(mod_id=rep(models[i]))#%>% -->
<!--     #mutate(timestep_within_day = replace(timestep_within_day, timestep_within_day == 0, 72)) -->
<!--   # add to list  -->
<!--   pattern_list[[i]]<-cur_mod -->
<!-- } -->

<!-- # bind them all together in a dataframe  -->
<!-- pattern_df<-bind_rows(pattern_list) -->

<!-- ``` -->

<!-- #### **Possibility to plot variables both within and between days** -->
<!-- I'm not sure if this is a useful way of showing the variables. It could be to show if there are 'extremes' at the start/end or if things are pretty consisten throughout the simulation.  -->
<!-- ```{r plot the ridgeline plots, include=T, message=F, warning=F, echo=F, fig.width=11, fig.height=17} -->
<!-- # Set the variables of interest  -->
<!-- #env_type_cur<-"6" -->
<!-- mod_id_cur<-"31" -->

<!-- plot_list<-list() -->

<!-- for (i in 1:12){ -->
<!--   cur_env_type<-i -->
<!--   # set the current env_type -->
<!--   # Make the graph  -->
<!--   df<-pattern_df[pattern_df$id==int_var,] -->
<!--   df<-df%>%filter(mod_id==mod_id_cur)%>% -->
<!--     filter(env_id==cur_env_type)%>% -->
<!--     filter(timestep_within_day<26) -->

<!--   # Now reformat this into a matrix with the right values  -->
<!--   mat<-matrix(NA, nrow=26, ncol=days) -->
<!--   mat[1:26, 1:days]<-df$value -->
<!--   #mat<-as.data.frame(mat) -->

<!--   axx<-list(title="Day in Sim") -->
<!--   axy<-list(title="Ts in day") -->
<!--   axz<-list(title=paste(int_var)) -->

<!--   surPlot<-plot_ly(z=~mat, scene=paste0("scene", i))%>%layout(title=list(text=paste0("Var=", int_var, " - Mod=", mod_id_cur))) -->
<!--   surPlot<-surPlot%>%add_surface(showscale=FALSE) -->
<!--   #%>% layout(scene=list(xaxis=axx, yaxis=axy, zaxis=axz)) #, title=list(text=paste0("Environment=", env_type_cur, " - Model=", mod_id_cur))) -->
<!--   #surPlot   -->
<!--   #print(i) -->
<!--   plot_list[[cur_env_type]]<-plotly_build(surPlot) -->
<!-- } -->

<!-- #fig<-subplot(plot_list, nrows=6, margin=0.05) -->



<!-- fig<-subplot(plot_list[[1]], plot_list[[2]], plot_list[[3]], plot_list[[4]],  plot_list[[5]], plot_list[[6]], plot_list[[7]], plot_list[[8]], plot_list[[9]], plot_list[[10]], plot_list[[11]], plot_list[[12]])%>% -->
<!--   layout( -->
<!--         scene = list(domain=list(x=c(0,0.5),y=c(0.83333333,1)), -->
<!--                       xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                       aspectmode='cube'), -->
<!--          scene2 = list(domain=list(x=c(0.5,1),y=c(0.83333333,1)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--          scene3 = list(domain=list(x=c(0,0.5),y=c(0.66666666666666666,0.83333333)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--          scene4 = list(domain=list(x=c(0.5,1),y=c(0.66666666666666666,0.83333333)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--           scene5 = list(domain=list(x=c(0,0.5),y=c(0.5,0.66666666666666666)), -->
<!--                       xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                       aspectmode='cube'), -->
<!--          scene6 = list(domain=list(x=c(0.5,1),y=c(0.5,0.66666666666666666)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--          scene7 = list(domain=list(x=c(0,0.5),y=c(0.333333333,0.5)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--          scene8 = list(domain=list(x=c(0.5,1),y=c(0.333333333,0.5)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--         scene9 = list(domain=list(x=c(0,0.5),y=c(0.16666666,0.333333333)), -->
<!--                       xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                       aspectmode='cube'), -->
<!--          scene10 = list(domain=list(x=c(0.5,1),y=c(0.16666666,0.333333333)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--          scene11 = list(domain=list(x=c(0,0.5),y=c(0,0.16666666)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube'), -->
<!--          scene12 = list(domain=list(x=c(0.5,1),y=c(0,0.16666666)), -->
<!--                        xaxis=axx, yaxis=axy, zaxis=axz, -->
<!--                        aspectmode='cube')) -->

<!-- #, plot_list[[5]], plot_list[[6]], plot_list[[7]], plot_list[[8]], plot_list[[9]], plot_list[[10]], plot_list[[11]], plot_list[[12]]) -->

<!-- #fit -->

<!-- fig -->

<!-- ``` -->







